String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-11 2023-1-19/sections/implementation.tex
experiment decripption be consistent with the result

Our experiments utilize two benchmark suites, namely, AutomatArk and RegCoL. In total, there are 49,379 instances in the two benchmark suites. All the benchmark instances are in SMTLIB2 format.

\paragraph*{AutomatArk benchmark suite.}
The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraint $|x| > 10$ (where $x$ is a string variable). There are 8,751 instances in the AutomatArk suite here.
Note that the original AutomatArk benchmark suite in \cite{z3str3re} includes 19,979 instances in total, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}. 
%Only 8,751 ones that contain counting operators out of 19,979 instances.

@@

Q1 is answered by running OSTRICH$^{\rm RECL}$ and the aforementioned solvers on AutomatArk and RegCoL. The experimental results can be found in Table~\ref{tab:results_all}. From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solves 49,483 instances correctly, which is 4,253/2,561/27,184/13,787/1,407/\zhilin{xxx} more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
%    
Note that Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth. If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance. 
%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
%
Moreover, OSTRICH$^{\rm RECL}$ is almost as fast as the fastest solver Z3str3RE. More specifically, OSTRICH$^{\rm RECL}$ spends 1.77 seconds per instance on average, while Z3str3RE spends 1.61 seconds per instance, while the other solvers spend at least 3 seconds per instance.  
Z3-Trau reports ``unknown'' on 21,152 instances, which is mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.

>>>>

Our experiments utilize two benchmark suites, namely, AutomatArk and RegCoL. In total, there are 48,834 instances in the two benchmark suites. All the benchmark instances are in SMTLIB2 format.

\paragraph*{AutomatArk benchmark suite.}
The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraint $|x| > 10$ (where $x$ is a string variable). There are 8,215 instances in the AutomatArk suite here.
Note that the original AutomatArk benchmark suite in \cite{z3str3re} includes 19,979 instances in total, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}. 
%Only 8,751 ones that contain counting operators out of 19,979 instances.

@@

Q1 is answered by running OSTRICH$^{\rm RECL}$ and the aforementioned solvers on AutomatArk and RegCoL. The experimental results can be found in Table~\ref{tab:results_all}. From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solves 48,689 instances correctly, which is 3,982/2,263/24,568/12,823/1,082/7083\zhilin{xxx} more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
%    
Note that Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth. If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance. 
%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
%
Moreover, OSTRICH$^{\rm RECL}$ is almost as fast as the fastest solver Z3str3RE. More specifically, OSTRICH$^{\rm RECL}$ spends 2.93 seconds per instance on average, while Z3str3RE spends 1.71 seconds per instance, while the other solvers spend at least 3 seconds per instance.  
Z3-Trau reports ``unknown'' on 21,655 instances, which is mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
